Group assignment

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

```{r echo=FALSE}
kable(count(df2, month)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.

@@

@@

@@

>>>>

```{r echo=FALSE}
kable(count(df2, month)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```
###2. There is no statistically significant difference in the price of hotels between summer and winter season
```{r echo=FALSE}
t.test(df2$trueprice [df2$season=="winter"],df2$trueprice [df2$season=="summer"], mu=0, alt='two.sided', conf=0.95, paired=F)
#Null Hypothesis is rejected

@@

## Time
### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.

@@

## Hypothesis testing for Time

###1. Is there any statistical significant difference in the hotel price per night between year 2017 and 2018
```{r echo=FALSE}
t.test(df2$trueprice [df2$year=="2017"],df2$trueprice [df2$year=="2018"], mu=0, alt='two.sided', conf=0.95, paired=F)
#(welsch1)
#Null Hypothesis is rejected though the t-statistic is insignificant 
```

## Country

@@

## Distance

@@

###1. Find the correlation between truelprice and distance 
```{r echo=FALSE}
corr_table1 <- df2 %>% 
  select(country, trueprice, distance) %>% 
  group_by(country) %>% 
  summarise(correlation = cor(trueprice,distance))
```

```{r echo=FALSE}
kable(corr_table1)
```
# Graph to show the correlation pattern by each country:
```{r echo=FALSE}
ggplot(corr_table1, aes(x = correlation ,
                       y = fct_reorder(country, correlation))) +
  geom_point(color = 'red', size = 2)+
  labs(y='Countries',x='Correlation')
```

#### As we may see, staying in the center is less valued in Austria and Slovakia.

###2. Find the correlation between guest reviewing report with distance and price
```{r echo=FALSE}
corr_table2 <- cor(df2[, c('trueprice','actualrating','distance')])
```
```{r echo=FALSE}
kable(corr_table2)
```
